Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
adding lemma for effective divisors adding a point with no new generator in degree 1

\begin{example}
\label{eg:g_1_deg_third}
Let $L = P - Q + \frac{1}{3}R$. Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$. For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next, 
We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q + 2R.$
\end{example}

@@

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
generator $u$ in degree 1; let $u$ \todo{Was there supposed to be something else in this sentence?}.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\delta$ with relations generated 
in degree at most $\tau $.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
that

@@

\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\delta,\beta)$ with relations generated in degree at most $\max(\tau,\delta+\beta,2\beta)$
\end{rem}

@@

\todo{Add higher genus corollaries once we figure out what we want to say there}

>>>>

\begin{example}
\label{eg:g_1_deg_third}
Let $L = P - Q + \frac{1}{3}R$. Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$. For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next, 
We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{Peter: Why don't we have something in degree 4?}
\end{example}

@@

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
generator $u$ in degree 1.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
that

@@

\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
\end{rem}

@@

\todo{Move this lemma:}
\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.  
Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\tau $.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$
